%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Software architect \& developer} % Job title
  {Freelance.} % Organization
  {Italy} % Location
  {Oct. 2023 - Oct. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Designed, developed and maintained a Rust back-end service
      \& relational database for the Pathfinder 2E TTRPG.}
    \item {Designed and developed a real-time face recognition
        software running on low end hardware like Raspberry PI without
      GPU, using Rust \& ONNX.}
    \end{cvitems}
  }


  %---------------------------------------------------------
  \cventry
  {DevOps, Software architect \& developer} % Job title
  {Formula SAE Pisa.} % Organization
  {Italy} % Location
  {Oct. 2023 - Jun. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Led the migration of the Formula SAE codebase and
      continuous integration from a self-hosted GitLab instance to GitHub.}
    \item {Developed a real-time library for calculating the optimal
      lap of a racing car, using Rust with Zenoh for communication with ROS2.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Back-end Junior Developer} % Job title
  {Zextras.} % Organization
  {Vicenza, Italy} % Location
  {Oct. 2021 - Oct. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Designed and developed a micro-service responsible of
        real-time preview of files, converting from any format to
        Image/PDF. Focus of the project was scalability,
        maintainability and the possibility to change any component
        underneath with as little refactor as possible. During the
        development of the software, optimizing IO operations, its
      performance was doubled.}
    \item {Refactored and completed a desktop application, using
        Python, to sync files with a remote server. This application
        was developed and deployed on all the possible Desktop
        operating systems. Worked on the GUI and the underlying logic
        of the program as well, in close contact with the UX/UI team.
        The project started as a R\&A mock and was later optimized,
      halving network calls and reducing average synchronization time by 25\%.}
    \item {Deployed static analysis tools in every python project, to
        ensure maintainability and strong type checking. Pioneered
        tools that got adopted by the company, standardizing codebase
        and cutting down development time. Adoption in the preview
      project resulted in reducing static analysis errors from 130 to 0.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Intern - Software Developer} % Job title
  {Yarix S.r.l.} % Organization
  {Montebelluna, Italy} % Location
  {Jun. 2021 - Aug. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Analyzed and developed a smart web-crawler capable of
        crawling through clear and dark web (Tor \& I2P) that would
        search for specified data, usually a company stolen assets.
        This software was developed for the Bachelor's thesis and was
      widely used even after my time with the company was over.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Intern - Mobile Developer} % Job title
  {Glow new media.} % Organization
  {Liverpool, United Kingdom} % Location
  {Jul. 2017 - Exp. Aug. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Researched and developed an application using Xamarin. The
        goal of the project was to research all the possible ways to
        keep track of how many steps a user would make. Successfully
      achieved the goal, empowering the company to test future initiatives.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
